Self Regulation Ontology Retest Data Report

### 2018-02-18 code/SRO_Report.Rmd
updating report w new data release

@@

boot_df = boot_df %>%
  drop_na() %>%
  mutate(icc = as.numeric(as.character(icc)),
         spearman = as.numeric(as.character(spearman)),
         eta_sq = as.numeric(as.character(eta_sq)),
         sem = as.numeric(as.character(sem)))

@@

# Check if you hae all variables bootstrapped
# retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]

@@

Plot flat estimates against

>>>>

```{r}
process_boot_df = function(df){
  df = df %>%
  drop_na() %>%
  mutate(dv = as.character(dv),
         icc = as.numeric(as.character(icc)),
         spearman = as.numeric(as.character(spearman)),
         eta_sq = as.numeric(as.character(eta_sq)),
         sem = as.numeric(as.character(sem)),
         partial_eta_sq = as.numeric(as.character(partial_eta_sq)),
         omega_sq = as.numeric(as.character(omega_sq)),
         var_subs = as.numeric(as.character(var_subs)),
         var_ind = as.numeric(as.character(var_ind)),
         var_resid = as.numeric(as.character(var_resid)),
         F_time = as.numeric(as.character(F_time)),
         p_time = as.numeric(as.character(p_time)),
         df_time = as.numeric(as.character(df_time)),
         df_resid = as.numeric(as.character(df_resid)))
  return(df)} 
```

@@

boot_df = process_boot_df(boot_df)

@@

# Check if you have all variables bootstrapped
# retest_report_vars[which(retest_report_vars %in% boot_df$dv==FALSE)]

# Boot df contains hddm parameters fit on the full sample in the t1 data
# refits_bootstrap_merged.csv.gz contains bootstrapped reliabilities

refit_boot_df = read.csv(gzfile(paste0(retest_data_path,'refits_bootstrap_merged.csv.gz')))

refit_boot_df = process_boot_df(refit_boot_df)

fullfit_boot_df = boot_df[as.character(boot_df$dv) %in% unique(as.character(refit_boot_df$dv)),]

boot_df = boot_df[!as.character(boot_df$dv) %in% unique(as.character(refit_boot_df$dv)),]

boot_df = rbind(boot_df, refit_boot_df)

rm(refit_boot_df)

@@

Plot flat estimates against hierarhical estimates.

Check the distributions of the flat and hierarchical estimates, transform if not normal and t-test to check if they are different than each other (alternatively get difference scores and check if they are different than 0/plot the distribution of the difference scores)
